\section{Introduction (TEMP nu van GPT)}

Magnetic skyrmions are topologically protected spin textures that have attracted considerable attention due to their unique physical properties and potential applications in spintronic devices. First proposed in the context of nuclear physics, skyrmions were later discovered in magnetic systems where competing interactions stabilize non-trivial spin configurations. Their small size, stability, and low current-driven mobility make them promising candidates for future information storage and processing technologies.

The formation of magnetic skyrmions is generally attributed to the competition between ferromagnetic exchange interactions and chiral spin-orbit coupling terms. In particular, the Dzyaloshinskii--Moriya interaction (DMI) favors twisted spin configurations, while the Heisenberg exchange interaction promotes parallel alignment of neighboring spins. An external magnetic field further influences the magnetic phase diagram by favoring spin alignment along its direction. The interplay between these interactions can give rise to a rich variety of magnetic phases, including ferromagnetic states, spin spirals, and skyrmion lattices.

In this work, we investigate the emergence and stability of skyrmionic configurations in a two-dimensional classical spin lattice described by a Heisenberg--Dzyaloshinskii--Moriya Hamiltonian. The system consists of unit-vector spins arranged on a square lattice with periodic boundary conditions. The Hamiltonian contains a ferromagnetic nearest-neighbor exchange interaction of strength $J$, a Dzyaloshinskii--Moriya interaction of strength $D$, and an external magnetic field $H_z$ applied perpendicular to the lattice plane.

To explore the phase space of the model, Monte Carlo simulations are performed over a range of Dzyaloshinskii--Moriya interaction strengths and magnetic field values. For each parameter set, the system is annealed through a sequence of inverse temperatures until a stable configuration is obtained. The resulting spin textures are analyzed using a discretized topological charge, computed from the solid angles subtended by neighboring spins on lattice plaquettes. This discretized winding number provides a robust measure of the skyrmion number and allows the identification of topologically non-trivial states on the lattice.

The primary objective of this study is to determine how the competition between chiral interactions and magnetic field strength influences the formation, number, and stability of skyrmions. By systematically sweeping the parameters $D$ and $H_z$, we construct a numerical overview of the regions in parameter space where skyrmionic phases emerge and investigate the associated topological properties of the resulting spin configurations.